---
title: "Lab_8"
author: "QRME Cohort!"
date: "11/10/2021"
output:
  pdf_document: 
    toc: true
    toc_depth: 3
    highlight: tango
    df_print: paged
bibliography: hw8references.bib 
#csl: chicago-annotated-bibliography.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5, 
                      fig.height = 8)
```

\newpage # Commit 1

```{r load library}

library(here)
library(janitor)
library(rio)
library(knitr)
library(tidyverse) #ggplot2 and dplyr are already present in tidyverse

# These packages are not used here
#library(dplyr)
#library(ggplot2)
#library(readr) 
#library(psych)
#library(magrittr)
#library(tinytex)

theme_set(theme_minimal())
```

```{r load data}
star <- import(here("data", "star.csv"), setclass = "tbl_df") %>%
  clean_names()

kable(head(star, 10)) #without kable this doesn't get printed in pdf
```

\newpage # Commit 2

Prior literature that explores environmental factors that influence academic achievement
finds that economic status [@barry2006effect; @considine2002influence] and gender [@hubbard2005role; @kukulu2013self] 
significantly influences academic achievement. 

@barry2006effect shows correlation between economic status and academic achievement in their study.

This paper utilized here [@herepackage], janitor [@janitorpackage], rio [@riopackage], knitr [@knitrpackage], and tidyverse [@tidyversepackage] packages from R for data cleaning and analysis. 

\newpage # Commit 3

**Summary statistics for students based on sex and free reduced lunch status**

*On average, students from low-income families with free/reduced lunch status regardless of their sex scored lower both in Math and Reading tests than their higher-income peers.*

```{r summary-stats}
sum <- star %>% 
    group_by(sex, frl) %>% 
    summarize(math_mean = mean(tmathss),
           math_sd = sd(tmathss),
           rdg_mean = mean(treadss),
           rdg_sd = sd(treadss)) %>%
      kable(digits = 2,
        booktabs = TRUE)
sum
```

\newpage # Commit 4

```{r plot}
ggplot(star, aes(x = totexp, y = tmathss)) +
    geom_point(color = "gray", alpha = 0.8) +
    geom_smooth(aes(color = frl), method = "lm") +
    labs(x = "Teacher Experience (in years)",
           y = "Total Math Scale Score",
           title = "Relation between teacher experience and math scores",
           subtitle = "Separate regression lines displayed by free/reduced price lunch status",
           color = "Lunch Status") +
    scale_color_manual(labels = c("Paid meals","Free/reduced price meals"),
                        values = c("lightcoral", "mediumturquoise"))+
    theme(legend.position="bottom") 
```
**Description:**

1. Though the regression lines have a positive slope, it almost looks flat. We can say that teacher's experience doesn't have much affect on student's math scale scores.    

2. Students with a lunch status of "Paid meals" score more than those on "Free/reduced price meals" status.


\newpage # References

